\vfill LiteCrypto

### 2014-12-12 paper/paper.tex
Initial add of Evaluation and Analysis section

>>>>

\subsection{Performance}
Because performance is dependent on instruction optimization, the most efficient programs are compiled specifically for a certain processor architecture. In order to reduce space, tweetNaCl cannot provide optimal run-time performance. \cite{TweetNaCl} While tweetNaCl is not fully optimized for the processor, the impact on a low-volume cryptographic communication like the CubeSat is minimal.
\subsubsection{-Os vs -O2 Optimization Flag}
Most typical applications use the -O2 flags for improved performance, but on a space limited platform, the -Os flag is more useful. The -Os flag enables all -O2 flags that typically do not increase size as well as performing more optimizations to reduce size. \cite{GCC} 
\subsection{Testing}
In order to ensure the functionality of the library, we tested generated our own test cases. We were able to verify, encrypt, and decrypt messages successfully. Due to a lack of proper hardware, the program was not tested live on a CubeSat and with actual packets. The other option besides testing directly on a CubeSat would be to test it against a CubeSat virtual machine, but the communications for the CubeSat require additional libraries that we were not provided. In this situation, we would provide the library to the CubeSat team and have them perform functionality tests according to their needs.
\subsection{Future Work}
While the initial library is completed, there are many features that can be added with minimal impact to the size constraints.
\subsubsection{Key Exchange by PKE}
If a key pair needs to be updated for some reason, we currently require direct access to the CubeSat in order to replace and verify the key. Because we currently use only the initial key pair, if the key was compromised, the CubeSat would be vulnerable to a user with malicious intent. In order to mitigate such risks, a key exchange algorithm should be implemented to allow the update of keys used for communication.
\subsubsection{Forward Secrecy}
Forward Secrecy would allow for past communications to stay private even when an attack is successful in compromising the private key. Because all the past communications were protected by forward secrecy, the attacker would not be able to decrypt previous messages. This is crucial if the CubeSat is communication confidential information.
\subsubsection{Sequence Numbers}
This would prevent replay attacks. Because communication to the Cubesat is not stable, packets are resent continuously while the cubesat is in range. This increases the chance that the Cubesat has received the packet. With unstable communication, if the Cubesat did receive the packet, a response packet may not be received by the sender. This form of communication means that the process of repeating the message to the Cubesat can cause a replay attack by an official source. While replaying a command may not affect the mission, there is concern when it is crucial for the Cubesat to receive the command only once. Such commands include movement, a concept that may be implemented in Cubesats in the future. If movement is implemented in the Cubesat, the Cubesat cannot be allowed to replay a movement otherwise there is the possibility the Cubesat can be knocked out of orbit or into another satellite. The simplest way to mitigate this risk is through sequence numbers. Because the official source would issue out one sequence number per command, a repeated packet would not affect the Cubesat once it parses the packet. As long as encryption remains secure, there is no concern over another entity forging a sequence number. This leads to the last case, a used sequence number with a different command. The only time this would happen through non-malicious means is if sequence number exceeds the amount of numbers allowed. In this situation, there should be some sort of authentication to alert the Cubesat that the sequence number should be reset. In the case of a sequence reset, measures should be taken so that an attacker collecting old packets cannot then send them to the Cubesat in attempts to get the Cubesat to perform a task.
